Representing and Reasoning About Spatial Regions Defined by Context

### 2012-01-21 code/scenarios/cdsr/trunk/papers/AAAI2012/evaluation.tex
baseline data

As a baseline, we will compare our results against the manually encoded CDSRs for the problem instance and the entire room. The precision and recall for considering the entire room provides a baseline from which to assess each of the questions. The performance of the manually encoded CDSRs evaluates how well the anchor points capture the user defined regions and a ceiling for the inferred region performance.

\from{Nick}{What are manually encoded CDSRs? Are these the ones you do and use for the base case?}

\subsection{Results}
\begin{table}
\caption{Performance by Room}
\begin{tabular}{|c|c|c|c|}
\hline
Room & Transfer & Manually Encoded & Entire Room \\
\hline
Classroom-1 & p=.6,r=1 & p=.7,r=.9 & p=.7,r=.9 \\
Classroom-1 & p=.6,r=1 & p=.7,r=.9 & p=.7,r=.9 \\
Classroom-1 & p=.6,r=1 & p=.7,r=.9 & p=.7,r=.9 \\
Classroom-1 & p=.6,r=1 & p=.7,r=.9 & p=.7,r=.9 \\
Classroom-1 & p=.6,r=1 & p=.7,r=.9 & p=.7,r=.9 \\
Studio-1 & p=.6,r=1 & p=.7,r=.9 & p=.7,r=.9 \\
\hline
\end{tabular}
\end{table}

\from{Nick}{Would this be just a single region type or averaging across all applicable ones?}

@@

\begin{table}
\caption{Performance by Region Type}
\begin{tabular}{|c|c|c|c|}
\hline
Region & Transfer & Manually Encoded & Entire Room \\
\hline
Front & p=.6,r=1 & p=.7,r=.9 & p=.7,r=.9 \\
Back & p=.6,r=1 & p=.7,r=.9 & p=.7,r=.9 \\
Front Rows & p=.6,r=1 & p=.7,r=.9 & p=.7,r=.9 \\
Back Rows & p=.6,r=1 & p=.7,r=.9 & p=.7,r=.9 \\
Kitchen & p=.6,r=1 & p=.7,r=.9 & p=.7,r=.9 \\
Office & p=.6,r=1 & p=.7,r=.9 & p=.7,r=.9 \\
\hline
\end{tabular}
\end{table}

@@

\begin{table}
\caption{Performance against Target Region}
\begin{tabular}{|c|c|c|}
\hline
Transfer & Manually Encoded & Entire Room \\
\hline
p=.6,r=1 & p=.7,r=.9 & p=.7,r=.9 \\
\hline
\end{tabular}
\end{table}

>>>>

As a baseline, we will compare our results against the manually encoded CDSRs for the problem instance and the entire room. The precision and recall for considering the entire room provides a baseline from which to assess each of the questions. The performance of the manually encoded CDSRs evaluates how well the anchor points capture the user defined regions and a ceiling for the inferred region performance.
\from{Klenk}{I think that I can do away with all of the stuff about the union from each of the subjects. Especially since we are averaging them all together anyways. We can have a variation in which we control for everything else and vary the user. Perhaps even another table...}

\from{Nick}{What are manually encoded CDSRs? Are these the ones you do and use for the base case?}
\from{Klenk}{Yes.}

\subsection{Results}
\begin{table}
\caption{Performance by Room}
\begin{tabular}{|c|c|c|c|}
\hline
Room & Transfer & Manually Encoded & Entire Room \\
\hline
Classroom-1 & p=nil,r=nil & p=.93,r=.60 & p=.23,r=1 \\
Classroom-2 & p=nil,r=nil & p=.90, r=.69 & p=.19,r=1 \\
Classroom-3 & p=nil,r=nil & p=.94,r=.64 & p=.17,r=1 \\
Classroom-4 & p=nil,r=nil & p=85,r=.89 & p=.19,r=1 \\  %This is 222-Classroom
Classroom-5 & p=nil,r=nil & p=.87,r=.71 & p=.24,r=1 \\ % This is 222-Seminar
Classroom-6 & p=nil,r=nil & p=.76,r=.66 & p=.20,r=.99 \\ % This is UG40
\hline
\end{tabular}
\end{table}

\from{Nick}{Would this be just a single region type or averaging across all applicable ones?}
\from{Klenk}{This is averaging across all applicable ones.}

@@

\begin{table}
\caption{Performance by Region Type}
\begin{tabular}{|c|c|c|c|}
\hline
Region & Transfer & Manually Encoded & Entire Room \\
\hline
Front & p=nil,r=nil & p=.89,r=.79 & p=.23,r=1 \\
Back & p=nil,r=nil & p=.85,r=.82 & p=.13,r=1 \\
Front Rows & p=nil,r=nil & p=.85,r=.48 & p=.22,r=1 \\
Back Rows & p=nil,r=nil & p=.94,r=.40 & p=.7,r=.9 \\
Kitchen & p=nil,r=nil & p=nil,r=nil & p=nil,r=nil \\
Office & p=nil,r=nil & p=nil,r=nil & p=nil,r=nil \\
\hline
\end{tabular}
\end{table}

@@

\begin{table}
\caption{Performance against Target Region}
\begin{tabular}{|c|c|c|}
\hline
Transfer & Manually Encoded & Entire Room \\
\hline
p=nil,r=nil & p=.88,r=.66 & p=.20,r=.99 \\
\hline
\end{tabular}
\end{table}
